Analysis of bulk void regions

### 2014-07-11 time-machine/cosmic_voids(29-05-14).tex
.

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Fractional anisotropy as tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sbustama@pegasus.udea.edu.co}$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

Since voids where discovered in the first compiled galaxy surveys 
\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
Kirshner87}, they have been identified as one of the most striking features 
of the Megaparsec universe, being a complementary aspect along with the 
filamentary and hierarchically clustered nature of the cosmic web 
\citep{Bond96}.

@@

We use here an unconstrained cosmological simulation, the Bolshoi 
simulation, to identify the possible large scale environment and 
cosmological voids.

The Bolshoi simulation follows the non-linear evolution of a dark matter 
density field on a cubic volume of size $250$\hMpc sampled with $2048^3$ 
particles. The cosmological parameters in the simulation are 
$\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}=0.73$, $h=0.70$, $n=0.95$ and 
$\sigma_{8}=0.82$ for the matter density, cosmological constant, 
dimensionless Hubble parameter, spectral index of primordial density 
perturbations and normalization for the power spectrum. The mass of each 
particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
We identify catalogues of halos through the Bound Density Maximum 
algorithm.

@@

@@

According to the classification scheme adopted for the cosmological 
environment, voids are regions where 
$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$. This implies that
the boundaries of void regions are controlled completely by the $\lambda_1$
eigenvalue of the web scheme and the threshold value. Therefore, as we 
increase the threshold value $\lambda_{th}$, all voids grow up 
progressively through contours of the $\lambda_1$ field until certain 
critical value where they are so large that the visual impression is no 
longer reproduced. Our objective here is to find a reliable quantity that 
allows to trace the geometry of void regions as classified by each web 
scheme. In the figure \ref{fig:L1_correlations} we calculate the 
distributions of the fractional anisotropy index and the density field 
regarding the $\lambda_1$ eigenvalue for both web schemes over all the 
cells of the simulation. Thick lines correspond to the median of the 
distributions, whereas coloured regions correspond to $50\%$ of the
sample, delimited by quartiles $Q_1$ and $Q_3$.

@@

\bibliographystyle{latex/mn2e}
\bibliography{references}

%.........................................................................
%Table of sizes of each sample defined in Bolshoi
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{l  r  r  r r} \hline\hline
	\textbf{Volume}					&				&\textbf{Scheme}& \\
	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\rho_{th}}$  \\ \hline
	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small Size of each sample defined in the Bolshoi 
  simulation and for each of the two schemes used to detect halos (FOF 
  and BDM).}

  \label{tab:Samples_Size}

\end{center}
\end{flushleft}
\end{table}
%.........................................................................

%.........................................................................
%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}

%.........................................................................
%FIGURE 3: Percolation Analysis
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.6\textheight]{./figures/voids_percolation_analysis.pdf}

  \captionof{figure}{\small Volume functions of voids catalogued by each 
  used scheme. Left panel (watershed transform over the FA field of the T-web 
  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
  (over the density field). Gray curves correspond to voids without boundary 
  removal whereas black curves are associated to voids merged through boundary 
  removal process. Dotted lines correspond to original continuous fields, 
  while segmented lines correspond to fields with a 1st-order median filtering 
  and continuous lines to a 2nd-order median filtering.}

%.........................................................................
%FIGURE 4: volume functions
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_regions_volume_all.pdf}

  \captionof{figure}{\small Volume functions of voids catalogued by each 
  used scheme. Left panel (watershed transform over the FA field of the T-web 
  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
  (over the density field). Gray curves correspond to voids without boundary 
  removal whereas black curves are associated to voids merged through boundary 
  removal process. Dotted lines correspond to original continuous fields, 
  while segmented lines correspond to fields with a 1st-order median filtering 
  and continuous lines to a 2nd-order median filtering.}

%.........................................................................
%FIGURE 5: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_density.pdf}

%.........................................................................
%FIGURE 6: shape-distributions
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 6mm 1mm 5mm 4mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/voids_inertia_tensor.pdf}

  \captionof{figure}{\small Volume functions of voids catalogued by each 
  used scheme. Left panel (watershed transform over the FA field of the T-web 
  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
  (over the density field). Gray curves correspond to voids without boundary 
  removal whereas black curves are associated to voids merged through boundary 
  removal process. Dotted lines correspond to original continuous fields, 
  while segmented lines correspond to fields with a 1st-order median filtering 
  and continuous lines to a 2nd-order median filtering.}

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Analysis of bulk void regions}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sbustama@pegasus.udea.edu.co}$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

The spatial distribution of galaxies describes a web-like pattern, the 
so-called cosmic web. Today it is understood that such configuration is 
driven by gravitational instabilities. ...

Relevant information about previous works and current state of the art.

@@

As it was previously mentioned, we use an unconstrained cosmological 
simulation, the Bolshoi simulation, to identify the possible large scale 
environment of the Local Group. This is a similar approach to the one already 
used by \SRKED{[reference here]}.

The Bolshoi simulation follows the non-linear evolution of a dark matter 
density field on a cubic volume of size $250$\hMpc sampled with $2048^3$ 
particles. The cosmological parameters in the simulation are 
$\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}=0.73$, $h=0.70$, $n=0.95$ and 
$\sigma_{8}=0.82$ for the matter density, cosmological constant, 
dimensionless Hubble parameter, spectral index of primordial density 
perturbations and normalization for the power spectrum. The mass of each 
particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
We identify halos with two algorithms, the Friends-of-Friends \SRKED{
[reference here]} algorithm and the Bound Density Maximum algorithm.

@@

%-------------------------------------------------------------------------
\subsection{Dark matter halos as tracers of the cosmic web 
\SRKED{(Possibly not included) [?]}}
\label{subsec:halos_cosmicweb}
%-------------------------------------------------------------------------

Both established schemes to quantify the cosmic web depend on continuous 
and smooth physical quantities, i.e the peculiar velocity field and the 
density field. To calculate these quantities, a discretization over the 
volume of the simulation is performed, so all the properties are reduced 
to single values associated to discrete cells. According to this, we 
divide the overall volume into $(256)^3$ cells, so each cell has an 
associated comoving cubic volume of $0.98 \mbox{ Mpc h}^{-1}$. Finally, in 
order to reduce possible effects due to the discretization process, a 
gaussian softening is performed between neighbour cells.

Once defined the numerical details about both classification schemes, we
shall analyse the dependence on the threshold value $\lambda_{th}$ for 
each one. For this, we shall use the distribution of dark matter halos as 
tracer of the underlying matter field in order to be more consistent with
available observational data. Therefore, we analyse distributions of mass 
and peculiar velocity in order to assign typical values to each type of 
environment. In the figure \ref{fig:typical_mass_velocity} we calculate 
both distributions for both web schemes and using the FOF catalogue of the 
simulation. Thick lines correspond to the median of the distribution and 
filled regions limited by dashed lines correspond to quartiles $Q_1$ and 
$Q_3$, it means, $50\%$ of all halos are within such regions for every 
\lth value and for each type of environment. We rather use median and 
quartiles as measure of dispersion because there are some very unusual 
and extreme values that makes the usual analysis based upon means and 
standard deviations less reliable.

A first interesting feature of the figure  \ref{fig:typical_mass_velocity} 
is the median mass for each region. In the case of the T-web, although 
dispersions of the distribution of mass for each environment are 
considerably overlapped each other, the median value is very 
well-differentiated among types of environment, indicating that it is 
possible to assign typical values of mass to each region, and being 
consistent with expectations, where low mass halos are typical in voids 
and higher mass halos in knots. For the case of the V-web scheme, all
medians and dispersions are completely overlapped, indicating that it is 
not possible to assign typical mass ranges to each environment as 
quantified by this scheme. For peculiar velocities, this situation is 
opposite, where V-web scheme is much more adequate to assign typical 
distributions of velocity to each environment. Although T-web also makes 
a differentiation in the distributions of velocity, this is very slight 
compared with the V-web case. These results can be explained by appealing 
the physical origin of each web scheme. As T-web is based upon the Hessian 
matrix of the potential field, it is expected all quantities related to 
the potential, like density field and distribution of halos mass, are 
well-differentiated among each region, while the V-web scheme, based upon 
the shear velocity tensor, all dynamical quantities, as the peculiar 
velocity field and the distribution of the velocity of halos are also 
expected to be well-differentiated among regions as quantified by this 
scheme.

Finally, we also calculate typical distributions of the density and 
peculiar velocity fields in each type of environment by using all cells of
the simulation grid instead of dark matter halos, obtaining completely
analogous results. Furthermore, we also use a BDM catalogue for the dark
matter halos, obtaining very similar results.

@@

According to the classification scheme adopted for the cosmological 
environment, voids are regions where 
$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$. This implies that
the boundaries of void regions are controlled completely by the $\lambda_1$
eigenvalue of the web scheme and the threshold value. Therefore, as we 
increase the threshold value $\lambda_{th}$, all voids grow up 
progressively through contours of the $\lambda_3$ field until certain 
critical value where they are so large that the visual impression is no 
longer reproduced. Our objective here is to find a reliable quantity that 
allows to trace the geometry of void regions as classified by each web 
scheme. In the figure \ref{fig:L1_correlations} we calculate the 
distributions of the fractional anisotropy index and the density field 
regarding the $\lambda_1$ eigenvalue for both web schemes over all the 
cells of the simulation. Thick lines correspond to the median of the 
distributions, whereas coloured regions correspond to $50\%$ of the
sample, delimited by quartiles $Q_1$ and $Q_3$.

@@

\bibliographystyle{mn2e}
\bibliography{references}

%.........................................................................
%FIGURE 1: Typical mass and pecular velocity
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Tweb.pdf}
  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Vweb.pdf}

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Tweb.pdf}
  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Vweb.pdf}

  \captionof{figure}{\small Distribution of masses of dark matter halos
  according the region where they are embedded for both web schemes 
  (upper panels) and of peculiar velocity (lower panels). It can be 
  noticed that the T-web scheme selects different mass ranges according
  to the environment, while the V-web scheme is better selecting ranges
  of peculiar velocity of the dark matter halos. This can be understood
  taking into account the physical origin of each web scheme.}

  \label{fig:typical_mass_velocity}
  \vspace{0.1 cm}

%.........................................................................
%FIGURE 2: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
  width=0.5\textheight]{./figures/cosmicweb_FA_Tweb.pdf}

  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
  width=0.5\textheight]{./figures/cosmicweb_FA_Vweb.pdf}

%.........................................................................
%FIGURE 3: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

@@
